Manifold Destiny - or how to rig an election

### 2024-02-11 presentation.qmd
break
abc
mone
worknow

---
title: "Manifold Destiny - or how to rig an election"
subtitle: "Based upon the ideas developed by Edward K. Solomon"
format:
  revealjs: 
    smaller: true
    toc-depth: 1
    toc: true 
execute: 
  cache: false
#webr: 
#  show-startup-message: true    # Disable displaying status of webR initialization
#  packages: ['dplyr','purrr','magrittr','data.table','tidyr'] # Install R packages on document open
##filters:
#- webr 
#footer: <https://lotariohw26.github.io/ManifoldDestiny/>
---

@@

**Our two stylized numerical example**

@@

Election outome 
```{r, echo=F}
#sum(dplyr::select(app_n_out[['rdfc']],S,U))/sum(dplyr::select(app_n_out[['rdfc']],S,T,U,V))
polynom::integral(round(polynom::polynomial(unname(pri_int_ex1))),c(0,1))
```

@@

Election outome
```{r, echo=F}
#sum(dplyr::select(app_ex1_out[['rdfc']],S,U))/sum(dplyr::select(app_ex1_out[['rdfc']],S,T,U,V))
polynom::integral(round(polynom::polynomial(unname(pos_int_ex1))),c(0,1))
```

>>>>

---
title: Manifold Destiny - or how to rig an election
#subtitle: "Based upon the ideas developed by Edward K. Solomon"
#format:
#  revealjs: 
#    smaller: true
#    toc-depth: 1
#    toc: true 
#execute: 
#  cache: false
#webr: 
#  show-startup-message: true    # Disable displaying status of webR initialization
#  packages: ['dplyr','purrr','magrittr','data.table','tidyr'] # Install R packages on document open
##filters:
#- webr 
#footer: <https://lotariohw26.github.io/ManifoldDestiny/>
---

@@

**Our two stylized numerical cases**

@@

Election outome 
```{r, echo=F}
#pri_int_ex1
#polynom::integral(round(polynom::polynomial(unname(pri_int_ex1))),c(0,1))
mean(app_ex1_cou$rdfc$alpha)
```

@@

Election outome
```{r, echo=F}
#polynom::integral(round(polynom::polynomial(unname(pos_int_ex1))),c(0,1))
pos_int_ex1
```
